\emph{Light Exposure Behavior Assessment (LEBA)}: Long and Short Form

### 2021-10-12 manuscript.Rmd
Flowchart1 Font

                    graph [layout = dot,fontsize = 20]

                     node[shape = rectangle, margin = 0.2, width = 6.5, height = 1, 
                    fixedsize = true,fontsize = 20]

@@

                    node[shape = rectangle, margin = 0.2, width = 6.5, height = 2, 
                    fixedsize = true, fontsize = 20]
                    C[label = 'Factor Identification
                    Scree Plot: 6 Factors
                    Parallel Analysis: 6 Factors
                    Minimum Average Partial Method: 5 Factors
                    Hull Method: 5 Factors']

                     subgraph cluster_1 {
                      graph[shape = rectangle]
                      style = rounded
                     node[ margin = 0.2,width = 7, height = 1, fixedsize = true, fontsize = 18 ]

@@

                    4[label = 'Confirmatory Factor Analysis 
                     on the Five Factor Model (23 Items; N=262)
                      Acceptable Fit ( CFI = .97; TLI .96; RMSEA = .04, SRMR = .09)']
                     5[label = 'Reliability Analysis on CFA (23 Items; N=262) 
                      Alpha F1=.93; F2=.80; F3 =.62; F4=.72; F5=.45']
                    }
                subgraph cluster_2 {
                      graph[shape = rectangle]
                      style = rounded
                     node[ margin = 0.2,width = 6.5, height = 1, fixedsize = true ]
                    6[label = '6-Factor  one factor with only two salient loadings']
                    7[label = 'Rejected']
                    }

                     edge[color = black,arrowhead = vee, arrowsize = 1.25]
                     A ->B
                     B ->C
                     C ->1
                     1 ->2
                     2 ->3
                     3 ->4
                     4 ->5
                     C ->6
                     6 ->7

>>>>

                    graph [fontname = Helvetica,layout = dot,fontsize = 20, ]

                     node[fontname = Helvetica, shape = rectangle, margin = 0.2, width = 6.5, height = 1, 
                    fixedsize = true,fontsize = 20]

@@

                    node[fontname = Helvetica, shape = rectangle, margin = 0.2, width = 7.5, height = 2, 
                    fixedsize = true, fontsize = 20]
                    C[label = 
                    <
                    Factor Identification<br align = 'left'/>
                    Scree Plot: 6 Factors<br align = 'left'/>
                    Parallel Analysis: 6 Factors<br align = 'left'/>
                    Minimum Average Partial Method: 5 Factors<br align = 'left'/>
                    Hull Method: 5 Factors<br align = 'left'/>
                    >
                    ]

                     subgraph cluster_1 {
                      graph[fontname = Helvetica, shape = rectangle]
                      style = rounded
                     node[fontname = Helvetica, margin = 0.2,width = 9, height = 1, 
                    fixedsize = true, fontsize = 18 ]

@@

                    4[label = 'Confirmatory Factor Analysis 
                     on the Five Factor Model (23 Items; N=262)
                      Acceptable Fit ( CFI = .97; TLI .96; RMSEA = .04, SRMR = .09)']
                     5[label = 'Reliability Analysis on CFA (23 Items; N=262) 
                      Alpha F1=.93; F2=.80; F3 =.62; F4=.72; F5=.45']
                    }
                subgraph cluster_2 {
                      graph[fontname = Helvetica,shape = rectangle]
                      style = rounded
                     node[fontname = Helvetica, margin = 0.2,width = 6.5, height = 1, 
                fixedsize = true, fontsize = 18 ]
                    6[label = '6-Factor  one factor with only two salient loadings']
                    7[label = 'Rejected']
                    }

                     edge[fontname = Helvetica,color = black,arrowhead = vee, arrowsize = 1.25]
                     A ->B
                     B ->C
                     C ->1
                     1 ->2
                     2 ->3
                     3 ->4
                     4 ->5
                     C ->6
                     6 ->7
